Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-07 WSSSPE2_report/WSSSPE2_review.tex
Section 4: Slight touch up.

%\item Samin Ishtiaq: Daemons, Notifications and Sustaining Software

>>>>

\item Samin Ishtiaq: Daemons, Notifications and Sustaining Software
%  Microsoft Research Cambridge

The reproduction and replication of novel results has become a major issue in
computer science, systems biology, and other computational disciplines. These
include both the inability to re-implement novel algorithms and approaches, and
lack of an agreement on how and what to benchmark these algorithms on.
Ishtiaq pointed out these problems and made several suggestions to address them.
